Irt plot extra

### 2022-09-19 manuscript_v2.Rmd
Table 3 updated with concise code

CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
colnames(CFa.matrix) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
CFa.matrix[1,] = c("Model 1", 
                   apa(as.numeric(cfa.sum.1$FIT[6]),2,T), 
                   apa(as.numeric(cfa.sum.1$FIT[7]),2,T), 
                   apa(as.numeric(cfa.sum.1$FIT[19]),2,F), 
                   apa(as.numeric(cfa.sum.1$FIT[20]),2,T),
                   apa(as.numeric(cfa.sum.1$FIT[27]),2,T),
                   apa(as.numeric(cfa.sum.1$FIT[28]),2,T),
                   apa(as.numeric(cfa.sum.1$FIT[29]),2,T),
                   apa(as.numeric(cfa.sum.1$FIT[35]),2,T))

CFa.matrix[2,] = c("Model 2", 
                   apa(as.numeric(cfa.sum.2$FIT[6]),2,T), 
                   apa(as.numeric(cfa.sum.2$FIT[7]),2,T), 
                   apa(as.numeric(cfa.sum.2$FIT[19]),2,F), 
                   apa(as.numeric(cfa.sum.2$FIT[20]),2,T),
                   apa(as.numeric(cfa.sum.2$FIT[27]),2,T),
                   apa(as.numeric(cfa.sum.2$FIT[28]),2,T),
                   apa(as.numeric(cfa.sum.2$FIT[29]),2,T),
                   apa(as.numeric(cfa.sum.2$FIT[35]),2,T))
```

```{r tabCfa, results='asis'}
apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items. Model 2 attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square.")
```

@@

```{r InvarianceTab, results='asis'}
apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )

>>>>

CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
colnames(CFa.matrix) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")

Cfa.matrix <- tabledown::cfa.tab.multi(fit.Cor.1,fit.Cor.2)
Cfa.matrix.selected <- as.data.frame(Cfa.matrix[, c(1,2,6,7,8,9,10,11)])
Cfa.matrix.selected <- tibble::rowid_to_column(Cfa.matrix.selected,"Model")
colnames(Cfa.matrix.selected) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")

```{r tabCfa}
apa_table(Cfa.matrix.selected, caption = "Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items. Model 2 attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square.")
```

@@

```{r InvarianceTab, results='asis'}
apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
